The problem and promise of scale in multilayer networks

### 2020-01-28 paper/manuscript.Rmd
acknowledgements

## Acknowledgements
* DCS
* check WG

>>>>

## Acknowledgements

We thank all members of the Wildlife Evolutionary Ecology Lab, including XXXXX **check WG reviewers** for their comments on previous versions of this manuscript as well as D. Schneider for inspiration and helpful discussions about scale. Funding for this study was provided by a Vanier Canada Graduate Scholarship to QMRW and a NSERC Discovery Grant to EVW.
